R Notebook

### 2016-08-01 finalwriteup/trial_code_eq.rmd
almost finished reading results and method

where $X_{j}$ is simply something

$X_{1}$, include the terms $X_{2} = X_1^2$ and $X_{3} = X_1^3$ to build a third degree polynomial. Interactions between explanatory variables can be modelled by including a terms such as $X_5 = X_4*X_1$

$\operatorname{logit}(p) = \log\left(\frac{p}{1-p}\right) = \log(odds)$

$p(ABCD) = p(C|ABD)\cdot p(A|BD) \cdot p(B|D) \cdot p(D)$

$p(ABCD) = p(C|BD)\cdot p(A|B) \cdot p(B) \cdot p(D)$

>>>>

$RMSE_b = \sqrt{\frac{\sum_{t = 1}^{n} (\widehat{y}_t - \bar y)^2}{n}}$

$$
\begin{aligned}
RMSE_b = \textrm{baseline root mean squared error} \\
n &= \textrm{number of data points} \\
\widehat{y} &= \textrm{predicted values of the response variable} \\
\bar y &= \textrm{mean 'return per dollar' for all projects} \\
\end{aligned}
$$

$\Delta\ error = RMSE_b - RMSE$
